%Acknowledgments

\renewcommand{\baselinestretch}{2}
\small\normalsize
\hbox{\ }
 
\vspace{-.65in}

\begin{center}
\large{Acknowledgments} 
\end{center} 

\vspace{1ex}


First and foremost, I'd like to thank my advisor Professor Carter Hall, for giving me the opportunity to have worked with him over the past years. I would have ended up in a boring nuclear engineering job had it not been for his intervention. He has always made time for me and has provided me with invaluable insight. I appreciate all your help over the years, I have learned a great deal from you.

I've been fortunate to have been surrounded by talented coworkers all who have helped me to become. Simon, Ruey, Clayton, Tom, Richard, Jon, Doug, I will cherish my graduate experience having worked in the lab with you all.

I would also like to thank Professor Richard Gaitskell and the entire group at Brown University, to whom I owe my familiarity with LUX data analysis and data processing. Jeremy, Dave, James, Monica, Carlos, Alastair, Simon F non of this analysis work would have been possible without your guidance. I would especially like to thank Carlos and his wife Fatma for their generosity.

I owe gratitude to all members of the LUX collaboration for contributing towards the development, construction and commissioning of the LUX detector. It was an enormous effort by all, and you built the most sensitive WIMP dark matter detector. Special thanks to Patrick, Markus, Jeremy, Carmen, Mongkol, Mia, Rachel, Nicole for making being onsite an amazing experience.

All of the personnel at the Sanford Underground laboratory in lead South Dakota deserve special mention. They keep our experiment running smoothing one mile underground, no easy task. 

I'd like to acknowledge all my friends who have helped take my mind off physics over the years. Henry, Kyle, Vibhu and Norvik. Special thanks to Kristy and Moose. Also, my friends in Hungary who always make sure I'm well fed and have a drink in my hand, Adam, Petya, N\'{a}ndi, Enik\H{o} and my cousin Zoli. 

My family members have always been there for me. I could not have made it with the support from my step father, grandparents, sister and mother. Szeretlek!



It is impossible to remember all so many people have helped me along the way, and I apologize to those I've inadvertently left out.





\begin{comment}

I owe my gratitude to all the people who have made this thesis possible and because of whom my graduate experience has been one that I will cherish forever.

First and foremost I'd like to thank my advisor, Professor Rajarshi Roy for giving me an invaluable opportunity to work on challenging and extremely interesting projects over the past four years. He has always made himself available for help and advice and there has never been an occasion when I've knocked on his door and he hasn't given me time. It has been a pleasure to work with and learn from such an extraordinary individual.

I would also like to thank my co-advisor, Dr. Parvez Guzdar. Without his extraordinary theoretical ideas and computational expertise, this thesis would have been a distant dream. Thanks are due to Professor Robert Gammon, Professor Edward Ott and Professor Thomas Antonsen for agreeing to serve on my thesis committee and for sparing their invaluable time reviewing the manuscript.

My colleagues at the nonlinear optics laboratory have enriched my graduate life in many ways and deserve a special mention. David DeShazer helped me start-off by rewriting the basic simulation code in a user-friendly format. Christian Silva provided help by setting up the GRENOUILLE apparatus and performing some of the simulations. My interaction with  Rohit Tripathi, Ryan McAllister, Vasily Dronov, Min-Young Kim, Elizabeth Rogers, William Ray, Jordi Garcia Ojalvo, Riccardo Meucci, Atsushi Uchida, and Fabian Rogister has been very fruitful. I'd also like to thank Wing-Shun Lam and Benjamin Zeff for providing the LaTex style files for writing this thesis.

I would also like to acknowledge help and support from some of the staff members. Donald Martin's technical help is highly appreciated, as is the computer hardware support from Edward Condon, LaTex and software help from Dorothea Brosius and purchasing help from Nancy Boone.

I owe my deepest thanks to my family - my mother and father who have always stood by me and guided me through my career, and have pulled me through against impossible odds at times. Words cannot express the gratitude I owe them. I would also like to thank Dr. Mohan Advani, Dr. Vasudeo Paralikar and Dr. Vinod Chaugule who are like family members to me.

My housemates at my place of residence have been a crucial factor in my finishing smoothly. I'd like to express my gratitude to Sivasankar Pandeti, Jayakumar Patil, Amit Trehan and Punyaslok Purakayastha for their friendship and support.

I would like to acknowledge financial support from the Office of Naval Research (ONR), Physics, for all the projects discussed herein.

It is impossible to remember all, and I apologize to those I've inadvertently left out.

Lastly, thank you all and thank God!


\end{comment}